---
title: "Global Test ANOVA 2"
author: "Jakub Liu"
date: "2024-12-06"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)
```


# Generate example data (just one dataset, no simulation yet)
```{r}
n <- 10
d <- 18
X <- data.frame(matrix(
  rnorm(n*d,0,1),
  nrow = n,
  ncol = d
))

X[,3] <- rnorm(n,100,1)
```



# The contrast and T matrix


```{r}
#if covariance_structure == 'unstructured'
Id <- matrix(rep(0,d*d), nrow = d, ncol = d)
diag(Id) <- 1
Jd <- matrix(rep(1,d*d), nrow = d, ncol = d)
Pd <- Id - (1/d)*Jd
H <- Pd
  
T_mat <- t(H)%*%ginv(H%*%t(H))%*%H
```

# Calculate the Yk vectors and the empirical covariance matrix
k --> index for the person\newline

```{r}
Y <- T_mat%*%t(X)

suma <- matrix(rep(0,d*d), nrow = d, ncol = d)

for(k in 1:n){
  suma <- suma + Y[,k]%*%t(Y[,k])
}

S_hat <- suma/n

```


# Calculate Ak, Akl, B0, B1 and B2
- each element of Ak and Akl is a scalar value, so Ak and Akl themselves are 1D vectors\newline
- A (Ak & Akl) is a n x n matrix, where n is the number of samples
- the diagonal elements of A are Ak and the off diagonal elements of A are Akl
- B0, B1, B2 are also scalar values\newline

```{r}

# calculate the A matrix (naive version)_____________________________________________________________
A <- matrix(rep(0,n*n), nrow = n, ncol = n)

for(k in 1:n){
  for(l in 1:n){
    A[k,l] <- t(Y[,k])%*%Y[,l]
  }
}

# more optimal version to calculate A
A_v2 <- apply(Y, 2, function(k) apply(Y, 2, function(l) t(k) %*% l))



# calculate B0_________________________________________________________________________________________
B0 <- sum(diag(A))/n  # is this correct?


# calculate B1 (naive version)_________________________________________________________________________-
diag_elems <- diag(A)
B1 <- 0

for(k in 1:n){
  for(l in 1:n){
    if(k!=l){
      B1 <- B1 + diag_elems[k]*diag_elems[l]
    }
  }
}

B1 <- B1/(n*(n-1))

# more optimal implementation of B1
B1_new <- sum(outer(diag_elems, diag_elems, function(k,l) ifelse(k==l, 0, k*l)))/(n*(n-1))



# calculate B2________________________________________________________________________________________
A_new <- A
diag(A_new) <- 0.0
A_new <- A_new^2
B2 <- sum(A_new)/(n*(n-1))

B0
B1
B1_new
B2
```

# Calcukate Qn and the test statistic (An)
```{r}
# cakculate Qn

Qn <- sum(A)/n
An <- Qn/B0
DegFree <- B1/B2
DegFree
```


# Calculate the pvalue
```{r}
pval <- pchisq(An, DegFree, lower.tail = FALSE, log.p = FALSE)
pval
```

