---
title: "Simulation_3_res_visualization"
author: "Jakub Liu"
date: "2025-03-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

```{r}
library(data.table)
library(ggplot2)
library(ggpubr)
```

```{r}
sim3 <- fread("C:/Users/Qba Liu/Documents/STUDIA/BIOINF_MASTER_BERLIN/MASTER_THESIS/SIMULATION_POLIGON/Sim3_full_parallel_output_table.csv")
View(sim3)

# the data needs to be reordered (wrong order of variables previously defined in expand.grid())
sim3_reordered <- sim3[order(rank(sim3$covariance_structures),
                    rank(sim3$sample_sizes),
                    rank(sim3$effect_sizes),
                    rank(sim3$n_iters_maxtest)) ,]

View(sim3_reordered)

```

# Stratify by covariance structure
```{r}
Unst <- sim3[sim3$covariance_structures == 'Unstructured',]
AR1 <- sim3[sim3$covariance_structures == 'AR(1)']
AR2 <- sim3[sim3$covariance_structures == 'AR(2)']
Toe <- sim3[sim3$covariance_structures == 'Toeplitz']
```

# Impact of the number of iterations (maxtest) on the power (of the maximum test)

Here I set the following variables to the following constant values.\newline
- sample size --> 10
- effect size --> 2

```{r}
plot1 <- ggplot(Unst[Unst$sample_sizes == 10 & Unst$effect_sizes == 2,], aes(x = n_iters_maxtest, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the number of iterations (Unstructured covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(AR1[AR1$sample_sizes == 10 & AR1$effect_sizes == 2,], aes(x = n_iters_maxtest, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the number of iterations (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot3 <- ggplot(AR2[AR2$sample_sizes == 10 & AR2$effect_sizes == 2,], aes(x = n_iters_maxtest, y = power_max)) +
  geom_point(color = "orange") + 
  geom_line(color = "orange", linetype = "dashed") +
  ggtitle("Power of the maximum test across the number of iterations (AR(2) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot4 <- ggplot(Toe[Toe$sample_sizes == 10 & Toe$effect_sizes == 2,], aes(x = n_iters_maxtest, y = power_max)) +
  geom_point(color = "magenta") + 
  geom_line(color = "magenta", linetype = "dashed") +
  ggtitle("Power of the maximum test across the number of iterations (Toeplitz covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, plot3, plot4, ncol = 2, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across its number of iterations", 
                                color = "black", face = "bold", size = 14))
```
# Impact of the sample size for the lowest and highest number of iterations

```{r}
min_iter <- sort(unique(sim3$n_iters_maxtest))[1]
max_iter <- sort(unique(sim3$n_iters_maxtest))[length(unique(sim3$n_iters_maxtest))]
```

## Unstructured covariance matrix

Here I set the following variables to the following constant values.\newline
- effect size --> 2
```{r}
plot1 <- ggplot(Unst[Unst$n_iters_maxtest == min_iter & Unst$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the number of sample sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(Unst[Unst$n_iters_maxtest == max_iter & Unst$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the number of sample sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the sample sizes for the minimum and maximum iteration number\n
                                (Unstructured covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```
## AR(1) covariance matrix
```{r}
plot1 <- ggplot(AR1[AR1$n_iters_maxtest == min_iter & AR1$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the sample sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(AR1[AR1$n_iters_maxtest == max_iter & AR1$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the sample sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the sample sizes for the minimum and maximum iteration number\n
                                (AR(1) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

## AR(2) covariance matrix
```{r}
plot1 <- ggplot(AR2[AR2$n_iters_maxtest == min_iter & AR2$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the sample sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(AR2[AR2$n_iters_maxtest == max_iter & AR2$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the sample sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the sample sizes for the minimum and maximum iteration number\n
                                (AR(2) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

## Toeplitz covariance matrix
```{r}
plot1 <- ggplot(Toe[Toe$n_iters_maxtest == min_iter & Toe$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the sample sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(Toe[Toe$n_iters_maxtest == max_iter & Toe$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the sample sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the sample sizes for the minimum and maximum iteration number\n
                                (Toeplitz covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```



# Impact of the effect size for the lowest and highest number of iterations

Here I set the following variables to the following constant values.\newline
- sample size --> 10

## Unstructured covariance matrix
```{r}
plot1 <- ggplot(Unst[Unst$n_iters_maxtest == min_iter & Unst$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(Unst[Unst$n_iters_maxtest == max_iter & Unst$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the effect sizes for the minimum and maximum iteration number\n
                                (Unstructured covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

## AR(1) covariance matrix
```{r}
plot1 <- ggplot(AR1[AR1$n_iters_maxtest == min_iter & AR1$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(AR1[AR1$n_iters_maxtest == max_iter & AR1$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the effect sizes for the minimum and maximum iteration number\n
                                (AR(1) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```


## AR(2) covariance matrix
```{r}
plot1 <- ggplot(AR2[AR2$n_iters_maxtest == min_iter & AR2$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(AR2[AR2$n_iters_maxtest == max_iter & AR2$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the effect sizes for the minimum and maximum iteration number\n
                                (AR(2) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```


## Toeplitz covariance matrix
```{r}
plot1 <- ggplot(Toe[Toe$n_iters_maxtest == min_iter & Toe$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 1000") +
  theme(plot.title = element_text(size = 7))

plot2 <- ggplot(Toe[Toe$n_iters_maxtest == max_iter & Toe$sample_sizes == 10,], aes(x = effect_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across the effect sizes for an iteration number of 20000") +
  theme(plot.title = element_text(size = 7))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the effect sizes for the minimum and maximum iteration number\n
                                (Toeplitz covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```