---
title: "Simulation 1 results visualization notebook"
author: "Jakub Liu"
date: "2025-02-17"
output: pdf_document
---

Offcourse these are non-exhaustive visualizations.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

```{r}
library(data.table)
library(ggplot2)
library(ggpubr)
```

# Simulation 1
```{r}
sim1 <- fread("C:/Users/Qba Liu/Documents/STUDIA/BIOINF_MASTER_BERLIN/MASTER_THESIS/SIMULATION_POLIGON/Simulation_1_parallel_table.csv")
head(sim1)
```

## Stratify by the covariance structure
```{r}
sim1_Unst <- sim1[sim1$covariance_structures == 'Unstructured']
sim1_AR1 <- sim1[sim1$covariance_structures == 'AR(1)']
sim1_AR2 <- sim1[sim1$covariance_structures == 'AR(2)']
sim1_Toe <- sim1[sim1$covariance_structures == 'Toeplitz']
```

### Unstructured covariance matrix
#### Plot the power across the sample sizes for each effect size


```{r}


plot1 <- ggplot(sim1_Unst[sim1_Unst$effect_sizes == 1,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_Unst[sim1_Unst$effect_sizes == 2,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_Unst[sim1_Unst$effect_sizes == 3,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Global test, Unstructured covmat", 
                                color = "black", face = "bold", size = 14))





plot1 <- ggplot(sim1_Unst[sim1_Unst$effect_sizes == 1,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_Unst[sim1_Unst$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_Unst[sim1_Unst$effect_sizes == 3,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Maximum test, Unstructured covmat", 
                                color = "black", face = "bold", size = 14))

```
### AR(1) covariance matrix
#### Plot the power across the sample sizes for each effect size

```{r}


plot1 <- ggplot(sim1_AR1[sim1_AR1$effect_sizes == 1,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_AR1[sim1_AR1$effect_sizes == 2,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_AR1[sim1_AR1$effect_sizes == 3,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Global test, AR(1) covmat", 
                                color = "black", face = "bold", size = 14))





plot1 <- ggplot(sim1_AR1[sim1_AR1$effect_sizes == 1,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_AR1[sim1_AR1$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_AR1[sim1_AR1$effect_sizes == 3,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Maximum test, AR(1) covmat", 
                                color = "black", face = "bold", size = 14))

```
### AR(2) covariance matrix
#### Plot the power across the sample sizes for each effect size

```{r}


plot1 <- ggplot(sim1_AR2[sim1_AR2$effect_sizes == 1,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_AR2[sim1_AR2$effect_sizes == 2,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_AR2[sim1_AR2$effect_sizes == 3,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Global test, AR(2) covmat", 
                                color = "black", face = "bold", size = 14))





plot1 <- ggplot(sim1_AR2[sim1_AR2$effect_sizes == 1,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_AR2[sim1_AR2$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_AR2[sim1_AR2$effect_sizes == 3,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Maximum test, AR(2) covmat", 
                                color = "black", face = "bold", size = 14))
```
### Toeplitz covariance matrix
#### Plot the power across the sample sizes for each effect size

```{r}


plot1 <- ggplot(sim1_Toe[sim1_Toe$effect_sizes == 1,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_Toe[sim1_Toe$effect_sizes == 2,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_Toe[sim1_Toe$effect_sizes == 3,], aes(x = sample_sizes, y = power_global)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the global test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Global test, Toeplitz covmat", 
                                color = "black", face = "bold", size = 14))





plot1 <- ggplot(sim1_Toe[sim1_Toe$effect_sizes == 1,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 1") +
  theme_minimal()

plot2 <- ggplot(sim1_Toe[sim1_Toe$effect_sizes == 2,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 2") +
  theme_minimal()

plot3 <- ggplot(sim1_Toe[sim1_Toe$effect_sizes == 3,], aes(x = sample_sizes, y = power_max)) +
  geom_point(color = "green") + 
  geom_line(color = "green", linetype = "dashed") +
  ggtitle("Power of the maximum test across sample sizes for the effect size of 3") +
  theme_minimal()



combined_plot <- ggarrange(plot1, plot2, plot3, ncol = 1, nrow = 3)
annotate_figure(combined_plot,
                top = text_grob("Maximum test, Toeplitz covmat", 
                                color = "black", face = "bold", size = 14))
```

