---
title: "large_sim1_results"
author: "Jakub Liu"
date: "2025-05-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is not an exhaustive visualization, just some preliminary visual inspection.
## Simulation parameters
### Variables
  - covariance structure
  - effect size (in the means)
  - sample size
### Simulation numbers
  - for each of the combinations of the variables the data was simulated 10,000 times
  - per simulation there where 10,000 Wild Bootstrap iterations as part of the maximum test
### Bradley Limits:
  - BL = 0.0457
  - BU = 0.0543
  - accuracy = 0.86%


```{r}
library(data.table)

data <- fread("C:/Users/Qba Liu/Documents/STUDIA/BIOINF_MASTER_BERLIN/MASTER_THESIS/MasterThesis_FUB/SIMULATIONS/SIMULATION_RESULTS/LARGE_SIMULATIONS/Simulation1_results.csv")
data$V1 <- NULL
Unst <- data[data$covariance_structures == 'Unstructured',]
AR1 <- data[data$covariance_structures == 'AR(1)',]
AR2 <- data[data$covariance_structures == 'AR(2)',]
Toeplitz <- data[data$covariance_structures == 'Toeplitz',]
```

```{r}
plot(Unst[Unst$effect_sizes == 2,]$sample_sizes, Unst[Unst$effect_sizes == 2, ]$power_global, col = 'blue', type = 'l', lwd = 4, xlab = 'sample size', ylab = 'power', main = 'Unstructured covariance matrix with an effect size of 2 (in the means)',
     cex.main = 1)
lines(Unst[Unst$effect_sizes == 2,]$sample_sizes, Unst[Unst$effect_sizes == 2, ]$power_max, col = 'red', type = 'l', lwd = 4)
grid()
legend("bottomright",                      
       legend = c('global test', 'MCTP + WildBoot'),
       col = c("blue", "red"),           
       lty = 1,                         
       lwd = 2)  
```





```{r}
plot(AR1[AR1$effect_sizes == 2,]$sample_sizes, AR1[AR1$effect_sizes == 2, ]$power_global, col = 'blue', type = 'l', lwd = 4, xlab = 'sample size', ylab = 'power', main = 'AR(1) covariance matrix with an effect size of 2 (in the means)',
     cex.main = 1)
lines(AR1[AR1$effect_sizes == 2,]$sample_sizes, AR1[AR1$effect_sizes == 2, ]$power_max, col = 'red', type = 'l', lwd = 4)
grid()
legend("bottomright",                      
       legend = c('global test', 'MCTP + WildBoot'),
       col = c("blue", "red"),           
       lty = 1,                         
       lwd = 2)   
```
```{r}
plot(AR2[AR2$effect_sizes == 2,]$sample_sizes, AR2[AR2$effect_sizes == 2, ]$power_global, col = 'blue', type = 'l', lwd = 4, xlab = 'sample size', ylab = 'power', main = 'AR(2) covariance matrix with an effect size of 2 (in the means)',
     cex.main = 1)
lines(AR2[AR2$effect_sizes == 2,]$sample_sizes, AR2[AR2$effect_sizes == 2, ]$power_max, col = 'red', type = 'l', lwd = 4)
grid()
legend("bottomright",                      
       legend = c('global test', 'MCTP + WildBoot'),
       col = c("blue", "red"),           
       lty = 1,                         
       lwd = 2)  
```
```{r}
plot(Toeplitz[Toeplitz$effect_sizes == 2,]$sample_sizes, Toeplitz[Toeplitz$effect_sizes == 2, ]$power_global, col = 'blue', type = 'l', lwd = 4, xlab = 'sample size', ylab = 'power', main = 'Toeplitz covariance matrix with an effect size of 2 (in the means)',
     cex.main = 1)
lines(Toeplitz[Toeplitz$effect_sizes == 2,]$sample_sizes, Toeplitz[Toeplitz$effect_sizes == 2, ]$power_max, col = 'red', type = 'l', lwd = 4)
grid()
legend("bottomright",                      
       legend = c('global test', 'MCTP + WildBoot'),
       col = c("blue", "red"),           
       lty = 1,                         
       lwd = 2)  
```

```{r}
plot(AR1[AR1$effect_sizes == 1,]$sample_sizes, AR1[AR1$effect_sizes == 1, ]$power_max, col = 'yellow', type = 'l', lwd = 4, xlab = 'sample size', ylab = 'power', main = 'Power of the maximum test across the effect sizes (in the means), AR(1) covariance matrix',
     cex.main = 0.8, ylim = c(0,1))
lines(AR1[AR1$effect_sizes == 1,]$sample_sizes, AR1[AR1$effect_sizes == 2, ]$power_max, col = 'orange', type = 'l', lwd = 4)
lines(AR1[AR1$effect_sizes == 1,]$sample_sizes, AR1[AR1$effect_sizes == 3, ]$power_max, col = 'red', type = 'l', lwd = 4)
grid()
legend("bottomright",
       legend = c('effect size 1', 'effect size 2', 'effect size 3'),
       col = c("yellow", "orange", "red"),
       lty = 1,
       lwd = 2)
```
```{r}
plot(AR1[AR1$effect_sizes == 1,]$sample_sizes, AR1[AR1$effect_sizes == 1, ]$power_global, col = 'yellow', type = 'l', lwd = 4, xlab = 'sample size', ylab = 'power', main = 'Power of the global test across the effect sizes (in the means), AR(1) covariance matrix',
     cex.main = 0.8, ylim = c(0,1))
lines(AR1[AR1$effect_sizes == 1,]$sample_sizes, AR1[AR1$effect_sizes == 2, ]$power_global, col = 'orange', type = 'l', lwd = 4)
lines(AR1[AR1$effect_sizes == 1,]$sample_sizes, AR1[AR1$effect_sizes == 3, ]$power_global, col = 'red', type = 'l', lwd = 4)
grid()
legend("bottomright",
       legend = c('effect size 1', 'effect size 2', 'effect size 3'),
       col = c("yellow", "orange", "red"),
       lty = 1,
       lwd = 2)
```

