---
title: "Sim_5_res_visualization_notebook"
author: "Jakub Liu"
date: "2025-03-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

```{r}
library(data.table)
library(ggplot2)
library(ggpubr)
```

```{r}
sim5 <- fread("C:/Users/Qba Liu/Documents/STUDIA/BIOINF_MASTER_BERLIN/MASTER_THESIS/SIMULATION_POLIGON/Sim5_full_parallel_output_table.csv")

# the data needs to be reordered (wrong order of variables previously defined in expand.grid())
sim5_reordered <- sim5[order(rank(sim5$covariance_structures),
                    rank(sim5$sample_sizes),
                    rank(sim5$dimensions),
                    rank(sim5$variance),
                    rank(sim5$correlation_abs)),]



# remove these conditions for which the covariance matrix is non-invertible
sim5_clean <- sim5_reordered[sim5_reordered$power_global != 'Covariance matrix non-invertible' & sim5_reordered$power_max != 'Covariance matrix non-invertible', ]
head(sim5_clean)
```


# Stratify by covariance structure
```{r}
Unst <- sim5_clean[sim5_clean$covariance_structures == 'Unstructured', ]
AR1 <- sim5_clean[sim5_clean$covariance_structures == 'AR(1)', ]
AR2 <- sim5_clean[sim5_clean$covariance_structures == 'AR(2)', ]
Toe <- sim5_clean[sim5_clean$covariance_structures == 'Toeplitz', ]
```

# Power by correlation
Here I fix the constants to the following values:
- sample size = 5
- dimensions = 5
- variance = 5

Here the plots are weird, but you can see where the power goes.

## Unstructured covariance matrix
```{r}
plot1 <- ggplot(Unst[
  Unst$sample_sizes == 5 &
  Unst$dimensions == 5 &
  Unst$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (Unstructured covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(Unst[
  Unst$sample_sizes == 5 &
  Unst$dimensions == 5 &
  Unst$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (Unstructured covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (Unstructured covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```


# AR(1) covariance matrix
```{r}
plot1 <- ggplot(AR1[
  AR1$sample_sizes == 5 &
  AR1$dimensions == 5 &
  AR1$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(AR1[
  AR1$sample_sizes == 5 &
  AR1$dimensions == 5 &
  AR1$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (AR(1) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

# AR(2) covariance matrix
```{r}
plot1 <- ggplot(AR2[
  AR2$sample_sizes == 5 &
  AR2$dimensions == 5 &
  AR2$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(AR2[
  AR2$sample_sizes == 5 &
  AR2$dimensions == 5 &
  AR2$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (AR(2) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```
```{r}
View(Toe)
```

# Toeplitz covariance matrix
```{r}
plot1 <- ggplot(Toe[
  Toe$sample_sizes == 5 &
  Toe$dimensions == 5 &
  Toe$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(Toe[
  Toe$sample_sizes == 5 &
  Toe$dimensions == 5 &
  Toe$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (AR(1) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

# Power by correlation (now with a much greater sample size)
Here I fix the constants to the following values:
- sample size = 91
- dimensions = 5
- variance = 5

## Unstructured covariance matrix
```{r}
plot1 <- ggplot(Unst[
  Unst$sample_sizes == 91 &
  Unst$dimensions == 5 &
  Unst$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (Unstructured covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(Unst[
  Unst$sample_sizes == 91 &
  Unst$dimensions == 5 &
  Unst$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (Unstructured covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (Unstructured covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

# AR(1) covariance matrix
```{r}
plot1 <- ggplot(AR1[
  AR1$sample_sizes == 91 &
  AR1$dimensions == 5 &
  AR1$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(AR1[
  AR1$sample_sizes == 91 &
  AR1$dimensions == 5 &
  AR1$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (AR(1) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```
# AR(2) covariance matrix
```{r}
plot1 <- ggplot(AR2[
  AR2$sample_sizes == 91 &
  AR2$dimensions == 5 &
  AR2$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(AR2[
  AR2$sample_sizes == 91 &
  AR2$dimensions == 5 &
  AR2$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (AR(2) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```

# Toeplitz covariance matrix
```{r}
plot1 <- ggplot(Toe[
  Toe$sample_sizes == 91 &
  Toe$dimensions == 5 &
  Toe$variance == 5,
], aes(x = correlation_abs, y = power_max)) +
  geom_point(color = "blue") + 
  geom_line(color = "blue", linetype = "dashed") +
  ggtitle("Power of the maximum test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

plot2 <- ggplot(Toe[
  Toe$sample_sizes == 91 &
  Toe$dimensions == 5 &
  Toe$variance == 5,
  ], aes(x = correlation_abs, y = power_global)) +
  geom_point(color = "red") + 
  geom_line(color = "red", linetype = "dashed") +
  ggtitle("Power of the global test across the correlation value (AR(1) covariance matrix)") +
  theme(plot.title = element_text(size = 5))

combined_plot <- ggarrange(plot1, plot2, ncol = 1, nrow = 2)
annotate_figure(combined_plot,
                top = text_grob("Power of the maximum test across the corelation\n
                                (AR(1) covariance matrix)", 
                                color = "black", face = "bold", size = 10))
```